Paper 2: survey analysis

### 2024-09-06 Rmd/Paper2.Rmd
Endret farger på figur.

```{r}
stolpediagram <- ggplot(dc, aes(x = studiested2, y = var, fill = studiested2)) +
  geom_bar(stat = "identity", position = "dodge") +
  # scale_fill_manual(values=viridis(3)) +
  geom_errorbar(aes(ymin = var - sd, ymax = var + sd), # se
    linewidth = .3, # Thinner lines
    width = .2,
    position = position_dodge(.9)
  ) +
  ggtitle("PCK, TK og TPACK fordelt på studiested") +
  guides(fill = "none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
  #  coord_cartesian(ylim = c(1,5)) +
  ylab("verdi") +
  xlab("studiested gruppe") +
  theme_bw() +
  facet_wrap(~TPACK)

print(stolpediagram) # vis plot
```

>>>>

```{r}
stolpediagram <- ggplot(dc, aes(x = studiested2, y = var, fill = studiested2)) +
  geom_bar(stat = "identity", position = "dodge") +
  #scale_fill_manual(values=viridis(3)) +
  scale_fill_manual(values=c("#812244", "#3fabb5", "#bee2e9")) +
  geom_errorbar(aes(ymin = var - sd, ymax = var + sd), # se
    linewidth = .3, # Thinner lines
    width = .2,
    position = position_dodge(.9)
  ) +
  ggtitle("PCK, TK og TPACK fordelt på studiested") +
  guides(fill = "none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
  #  coord_cartesian(ylim = c(1,5)) +
  ylab("verdi") +
  xlab("studiested gruppe") +
  theme_bw() +
  facet_wrap(~TPACK)

print(stolpediagram) # vis plot

#ggsave("../output/TPACK_stolpediagram_new.png")
```
